---
title: "Using the StudentPerformance Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the StudentPerformance package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(StudentPerformance)
```
## Reading Student Data
Use read_student_data() to import student performance data from a CSV file. 
```{r}
data <- read_student_data("student_data.csv")
head(data)

```

# OR
# Use sample data (if not reading from a file)

```{r}
# Create sample data
data <- data.frame(
  StudentID = 1:10,
  Subject = rep(c("Math", "Science", "History"), length.out = 10),
  Score = c(85, 92, 75, 88, 95, 60, 78, 89, 80, 91),
  StudyHours = c(3.5,2,4,2,3,1,5,3,2,1),
  Total = rep(100, 10),
  Date = as.Date('2023-01-01') + 0:9
)
```





## Calculating GPA
Use calc_gpa() to compute a student’s GPA using grade and credit columns.


```{r}
# Calculate GPA for each student based on their percentage score
data$GPA <- calc_gpa(calc_percentage(data$Score, data$Total))
print(data)

```
## Comparing Monthly Performance
Use compare_monthly() to examine how scores change over different months.


```{r}
compare_monthly(data)

```

## Course Summary Statistics
Use course_summary_stats() to get descriptive statistics for scores across different courses.

```{r}

course_summary_stats(data)

```
