---

title: "Using the StudentPerformance Package"
output: rmarkdown::html\_vignette
vignette: >
%\VignetteIndexEntry{Using the StudentPerformance package}
%\VignetteEngine{knitr::rmarkdown}
%\VignetteEncoding{UTF-8}
-------------------------

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(devtools)
devtools::load_all()
library(dplyr)
library(lubridate)
library(ggplot2)
```

## Reading Student Data

Use `read_student_data()` to import student performance data from a CSV file. This function reads a specified file if it exists or returns an empty data frame if the file is missing.

```{r}
data <- read_student_data("student_data.csv")
head(data)
```

### Creating Sample Data (Optional)

If you don't have a data file yet, you can create sample data to explore the package functionality:

```{r}
data <- data.frame(
  Date = as.Date(c("2025-04-01", "2025-04-04", "2025-04-10")),
  Subject = c("Math", "Biology", "Math"),
  Category = c("Exam", "Project", "Homework"),
  Score = c(88, 91, 76),
  Total = c(100, 100, 100),
  StudyHours = c(3.5, 3.5, 2.5),
  Semester = c("Spring 2025", "Spring 2025", "Spring 2025"),
  stringsAsFactors = FALSE
)
head(data)
```

## Course Summary Statistics

Use `course_summary_stats()` to get descriptive statistics for scores across different courses.

```{r}
course_summary_stats(data)
```

## Calculating GPA

To calculate GPA for each student, use the `calc_gpa()` function.

```{r}
data$GPA <- calc_gpa(calc_percentage(data$Score, data$Total))
head(data)
```

## Adding Cumulative GPA

If you want to track cumulative GPA over time, use the `add_metrics()` function.

```{r}
data <- add_metrics(data)
head(data)
```

## Saving Your Data

You can save your updated data to a CSV file with `write_student_data()`.

```{r}
write_student_data(data, "updated_student_data.csv")
```
