---
title: "Using the StudentPerformance Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the StudentPerformance package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(StudentPerformance)
```

Tracking Academic Performance with StudentPerformance
The StudentPerformance package provides tools for organizing, analyzing, and visualizing academic grades across multiple courses and timeframes.

In this vignette, we'll walk through a real-world example of how a student might use the package to:

1.Record their grades

2.Analyze performance by course

3.Compare course outcomes

4.Identify trends over time

Step 1: Create a Dataset
Suppose a student wants to track their weekly scores in three different courses over five weeks.

```{r}
initial_data <- data.frame(
  Date = as.Date(c("2025-03-01", "2025-03-05", "2025-03-10")),
  Subject = c("Math", "Biology", "Physik"),
  Category = c("Homework", "Exam", "Project"),
  Score = c(85, 90, 92),
  Total = c(100, 100, 100),
  StudyHours = c(2, 4, 3),
  Semester = c("Spring 2025")
)

```

Step 2: Analyze Average Performance by Course
A student may want to know which subject they are performing strongest in.

```{r}
average_score_by_course(student_data)
```
This function groups scores by subjct and returns the mean score for each subject.

Step 3: Visualize Score Trends
It can be helpful to visualize performance over time.


```{r}
 plot_gpa_over_time(student_data)
```

This would help identify whether performance is improving, declining, or consistent throughout the semester.

Step 4: Compare Two Specific Subjects
Maybe the student wants to compare how they’re doing in Math,Biology and Physics.

```{r}
course_summary_stats(student_data)
```

This comparison can help guide study strategies and time allocation.

Step 5: Track Weekly Improvements
A student may want to see whether there’s any improvement from Week 1 to Week 5 across all courses.

```{r}
library(dplyr)

grades %>%
  group_by(Week) %>%
  summarise(Avg_Grade = mean(Grade))
```


A rising average could indicate that the student is improving overall, which is motivating.

Summary
The StudentPerformance package allows students to take control of their academic journey by making grade data meaningful. With the ability to group, compare, and visualize performance, it serves as both a tracker and a diagnostic tool for improving study habits and outcomes.
