---
title: "Using the StudentPerformance package"
vignette: >
  %\VignetteIndexEntry{Using the StudentPerformance package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

```{r setup}
library(StudentPerformance)

```


## Reading Student Data

Use read_student_data() to import student performance data from a CSV file. This function reads a specified file if it exists or returns an empty data frame if the file is missing.

```{r}
data <- read_student_data("student_data.csv")
head(data)
```


Creating Sample Data (Optional)

If you don't have a data file yet, you can create sample data to explore the package functionality:

```{r}
data <- data.frame(
  Date = as.Date(c("2025-04-01", "2025-04-04", "2025-04-10")),
  Subject = c("Math", "Biology", "Math"),
  Category = c("Exam", "Project", "Homework"),
  Score = c(88, 91, 76),
  Total = c(100, 100, 100),
  StudyHours = c(3.5, 3.5, 2.5),
  Semester = c("Spring 2025", "Spring 2025", "Spring 2025"),
  stringsAsFactors = FALSE
)
head(data)
```


## Calculating GPA

Use `calc_gpa()` to turn raw percentages into a 4.0 GPA scale.  If your data doesn’t already have a \`Percentage\` column, compute it first:

```{r}
# Suppose `data` has Score and Total columns:
data$Percentage <- data$Score / data$Total * 100

# Now convert to GPA:
data$GPA <- calc_gpa(data$Percentage)

# View the first few rows
head(data)
#data$GPA <- calc_gpa(calc_percentage(data$Score, data$Total))
#head(data)
```


##Comparing Monthly Performance

To visualize monthly performance trends, use the compare_monthly() function.

```{r}
compare_monthly(data)
```


##Get Summary Statistics
Use course_summary_stats() to get descriptive statistics for scores across different courses.

```{r}
course_summary_stats(data)

```

##Saving Your Data
You can save your updated data to a CSV file with write_student_data().

```{r}
write_student_data(data, "updated_student_data.csv")
```

