---
title: "Using the StudentPerformance Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the StudentPerformance package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(StudentPerformance)
library(dplyr)
library(lubridate)
library(ggplot2)
```

## Reading Student Data
Use `read_student_data()` to import student performance data from a CSV file. This function reads a specified file if it exists or returns an empty data frame if the file is missing.

```{r}
data <- read_student_data("student_data.csv")
head(data)
```

### Creating Sample Data (Optional)
If you don't have a data file yet, you can create sample data to explore the package functionality:

```{r}
data <- data.frame(
  Date = as.Date(c("2025-04-01", "2025-04-04", "2025-04-10")),
  Subject = c("Math", "Biology", "Math"),
  Category = c("Exam", "Project", "Homework"),
  Score = c(88, 91, 76),
  Total = c(100, 100, 100),
  StudyHours = c(3.5, 3.5, 2.5),
  Semester = c("Spring 2025", "Spring 2025", "Spring 2025"),
  stringsAsFactors = FALSE
)
head(data)
```



## Comparing Monthly Performance
Use `compare_monthly()` to examine how scores change over different months.

```{r}
compare_monthly(data)
```

## Course Summary Statistics
Use `course_summary_stats()` to get descriptive statistics for scores across different courses.

```{r}
course_summary_stats(data)
```



